The role of cognateness in native spoken word recognition

### 2025-07-25 docs/appendix.qmd
Update repo

theme_set(theme_ggdist() +
  theme(panel.grid.major.y = element_line(
    colour = "grey",
    linetype = "dotted"
  )))

@@

list(exp_1_m0, exp_2_m0, exp_3_m1) |>
  set_names(paste0("Experiment ", 1:3)) |>
  map_dfr(gather_draws, `b_.*`, regex = TRUE, .id = "exp") |>
  dplyr::filter(.variable != "b_Intercept") |>
  mutate(
    .value = .value / 4,
    .variable = factor(.variable,
      levels = names(var_labels),
      labels = var_labels
    )
  ) |>
  ggplot(aes(.iteration, .value, colour = factor(.chain))) +
  facet_grid(.variable ~ exp, scales = "free") +
  geom_line() +
  labs(
    x = "Iteration",
    y = "Value",
    colour = "Chain",
    fill = "Chain",
    linetype = "Chain"
  ) +
  scale_colour_brewer(palette = "Reds") +
  theme(
    legend.position = "top",
    legend.box = "horizontal",
    panel.border = element_rect(
      fill = NA,
      colour = "grey"
    ),
    legend.justification = c(1, 0),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  )
```

@@

list(exp_1_m0, exp_2_m0, exp_3_m1) |>
  set_names(paste0("Experiment ", 1:3)) |>
  map_dfr(gather_draws, `b_.*`, regex = TRUE, .id = "exp") |>
  dplyr::filter(.variable != "b_Intercept") |>
  mutate(
    .value = .value / 4,
    .variable = factor(.variable,
      levels = names(var_labels),
      labels = var_labels
    )
  ) |>
  ggplot(aes(.value, reorder(exp, desc(exp)))) +
  facet_wrap(~.variable, scales = "free_x") +
  annotate(
    geom = "rect",
    xmin = -0.1 / 4,
    xmax = 0.1 / 4,
    ymin = -Inf,
    ymax = Inf,
    fill = "grey",
    alpha = 3 / 4,
    colour = NA
  ) +
  geom_vline(
    xintercept = 0,
    colour = "grey",
    linewidth = 3 / 4
  ) +
  stat_slab(aes(fill = after_stat(level)),
    point_interval = mode_hdi,
    .width = c(0.95, 0.89, 0.67, 1),
    outline_bars = TRUE,
    colour = "white",
    linewidth = 0.1,
    breaks = 20,
    normalize = "panels"
  ) +
  stat_spike(
    at = "median",
    size = 1,
    aes(linetype = "Median"),
    normalize = "panels"
  ) +
  labs(
    x = "Estimate", y = "Experiment",
    colour = "CrI",
    fill = "CrI",
    linetype = ""
  ) +
  scale_fill_brewer(palette = "Reds") +
  theme(
    legend.position = c(1, 0),
    legend.box = "horizontal",
    legend.justification = c(1, 0),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  )
```

>>>>

theme_set(
  theme_ggdist() +
    theme(
      panel.grid.major.y = element_line(
        colour = "grey",
        linetype = "dotted"
      )
    )
)

@@

list(exp_1_m0, exp_2_m0, exp_3_m1) |>
  set_names(paste0("Experiment ", 1:3)) |>
  map_dfr(gather_draws, `b_.*`, regex = TRUE, .id = "exp") |>
  dplyr::filter(.variable != "b_Intercept") |>
  mutate(
    .value = .value / 4,
    .variable = factor(
      .variable,
      levels = names(var_labels),
      labels = var_labels
    )
  ) |>
  ggplot(aes(.iteration, .value, colour = factor(.chain))) +
  facet_grid(.variable ~ exp, scales = "free") +
  geom_line() +
  labs(
    x = "Iteration",
    y = "Value",
    colour = "Chain",
    fill = "Chain",
    linetype = "Chain"
  ) +
  scale_colour_brewer(palette = "Reds") +
  theme(
    legend.position = "top",
    legend.box = "horizontal",
    panel.border = element_rect(
      fill = NA,
      colour = "grey"
    ),
    legend.justification = c(1, 0),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  )
```

@@

list(exp_1_m0, exp_2_m0, exp_3_m1) |>
  set_names(paste0("Experiment ", 1:3)) |>
  map_dfr(gather_draws, `b_.*`, regex = TRUE, .id = "exp") |>
  dplyr::filter(.variable != "b_Intercept") |>
  mutate(
    .value = .value / 4,
    .variable = factor(
      .variable,
      levels = names(var_labels),
      labels = var_labels
    )
  ) |>
  ggplot(aes(.value, reorder(exp, desc(exp)))) +
  facet_wrap(~.variable, scales = "free_x") +
  annotate(
    geom = "rect",
    xmin = -0.1 / 4,
    xmax = 0.1 / 4,
    ymin = -Inf,
    ymax = Inf,
    fill = "grey",
    alpha = 3 / 4,
    colour = NA
  ) +
  geom_vline(
    xintercept = 0,
    colour = "grey",
    linewidth = 3 / 4
  ) +
  stat_slab(
    aes(fill = after_stat(level)),
    point_interval = mode_hdi,
    .width = c(0.95, 0.89, 0.67, 1),
    outline_bars = TRUE,
    colour = "white",
    linewidth = 0.1,
    breaks = 20,
    normalize = "panels"
  ) +
  stat_spike(
    at = "median",
    size = 1,
    aes(linetype = "Median"),
    normalize = "panels"
  ) +
  labs(
    x = "Estimate",
    y = "Experiment",
    colour = "CrI",
    fill = "CrI",
    linetype = ""
  ) +
  scale_fill_brewer(palette = "Reds") +
  theme(
    legend.position = c(1, 0),
    legend.box = "horizontal",
    legend.justification = c(1, 0),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  )
```
